Title here

### 2017-05-24 portfolio/text/ms.Rmd
Final edits before resubmission

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.45\textwidth]{../figs/fig1-jk.pdf}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.45\textwidth]{../figs/stan-across-strategy-variability2.pdf}

@@

\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=0.65\textwidth]{../figs/stan-gg-spoke2.pdf}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.46\textwidth]{../figs/stan-offset-break-anti-spaghetti-specializing.pdf}

@@

There are many possible barriers to diversification for individuals relying on
natural resources for their livelihood. A primary barrier is the cost of
diversifying. For commercial fishers, purchasing additional licenses and gear
typically represents a substantial expense. Related barriers are apparent in
other natural resource sectors. For example, diversification has been positively
linked with total income or access to financial capital for farmers
[@abdulai2001; @barrett2001], small-scale fishing communities [@olale2012], and
those relying on forest resources [@illukpitiya2008].
<!-- Response to reviewer comment A2 -->
While we were unable to incorporate costs, it is possible that including them 
 <!-- license and gear purchase costs along with others such as costs of gear maintenance, catch transportation, and selling to a processor -->
would unveil a different relationship between catch diversification and profits than the relationships between catch diversification and revenue shown here.
Another major barrier to
diversification can be management restrictions. In commercial fisheries,
regulations that have been shown to reduce overfishing---including improved
assessments [@melnychuk2017] and individual quota systems 
[@costello2008]---may ultimately restrict individual diversification [@smith1986; @kasperski2013]
or at least make developing a diverse fishing portfolio more expensive. However,
individual quota systems, in particular, may also reduce income variability
(Fig. S\figifq A) perhaps offsetting the effects of reduced diversification
[@holland2016].

>>>>

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.45\textwidth]{fig1-jk.pdf}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.45\textwidth]{stan-across-strategy-variability2.pdf}

@@

\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=0.65\textwidth]{stan-gg-spoke2.pdf}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.46\textwidth]{stan-offset-break-anti-spaghetti-specializing.pdf}

@@

There are many possible barriers to diversification for individuals relying on
natural resources for their livelihood. A primary barrier is the cost of
diversifying. For commercial fishers, purchasing additional licenses and gear
typically represents a substantial expense. Related barriers are apparent in
other natural resource sectors. For example, diversification has been positively
linked with total income or access to financial capital for farmers
[@abdulai2001; @barrett2001], small-scale fishing communities [@olale2012], and
those relying on forest resources [@illukpitiya2008].
<!-- Response to reviewer comment A2 -->
While we were unable to incorporate costs, it is possible that 
including license and gear purchase costs along with others such as costs of
gear maintenance, catch transportation, and selling to a processor
would alter the relationship between catch diversification and profits.
<!-- unveil a different relationship between catch diversification and profits than the relationships between catch diversification and revenue shown here. -->
Another major barrier to
diversification can be management restrictions. In commercial fisheries,
regulations that have been shown to reduce overfishing---including improved
assessments [@melnychuk2017] and individual quota systems 
[@costello2008]---may ultimately restrict individual diversification [@smith1986; @kasperski2013]
or at least make developing a diverse fishing portfolio more expensive. However,
individual quota systems, in particular, may also reduce income variability
(Fig. S\figifq A) perhaps offsetting the effects of reduced diversification
[@holland2016].
